Poster figures

### 2025-03-07 analysis/poster_ncar/presentation_figures.Rmd
Figures for NCAR

```{r hindcast_extent}
hindcast_extent <- fread(here::here("data/derived/hindcast_extent.csv")) |> 
  _[, model := relevel(factor(model), "S2")] |> 
  _[, lag := as.numeric(as.Date(time) - as.Date(forecast_time))] |> 
  _[lag > 0] |> 
  _[!(month(forecast_time) == 1 & member == 7 & model == "S1")]  # This member is wrong
```

@@

@@

@@

clim_std2 |> 
  rbind(errors) |> 
  _[measure == "rmse"] |> 
  _[obs_dataset == which_dataset] |> 
  _[, .(rmse = median(value, na.rm = TRUE)), 
    by = .(time = update(time, year = 2001), 
           time_forecast = update(time_forecast, year = 2001), 
           lag,
           version)] |> 
  # _[version == "climatology"] |>
  ggplot(aes(time, rmse)) +
  geom_line(data = \(x) x[version == "climatology"],
            aes(group = interaction(time_forecast, month(time_forecast) <= month(time)))) +
  # geom_line(data = \(x) x[version == "S2"],
  #           aes(color = factor(month(time_forecast)),
  #               group = interaction(time_forecast, month(time_forecast) <= month(time)))) +
  # geom_point(data = \(x) x[version == "S2" & lag ==1], aes(color =  factor(month(time_forecast)))) +
  scale_color_manual(values = colorRampPalette(gglgbtq::palette_lgbtq("nonbinary")[c(1, 3, 4, 1)])(12),
                     aesthetics = c("fill", "color"), guide = "none") +
  scale_y_continuous(limits = c(0, NA)) +
  geom_vline(xintercept = as.Date("2001-02-28"))
```

>>>>

```{r hindcast_extent}
hindcast_extent <- fread(here::here("data/derived/hindcast_extent.csv")) |> 
  _[, model := relevel(factor(model), "S2")] |> 
  _[, lag := as.numeric(as.Date(time) - as.Date(forecast_time))] |> 
  _[lag > 0] |> 
  _[!(month(forecast_time) == 1 & member == 7 & model == "S1")]  # This member is wrong =
```

@@

hindcast_extent |> 
  copy() |> 
  _[, aice := aice - mean(aice[year(time) %between% c(1981, 2011)]), 
    by = .(lag, model, time = update(time, year = 2000))] |> 
  _[, .(forecast = mean(aice)), by = .(model, forecast_time, time = as.Date(round_date(time, "month")))] |> 
  _[, lag := months_difference(time, forecast_time)] |> 
  _[, merge(.SD, monthly_extent, all = TRUE), by = .(model, lag)] |> 
  _[time %between% s1_range] |> 
  _[, .(text = sqrt(mean((aice - forecast)^2, na.rm = TRUE))), by = .(lag, model, dataset)] |> 
  ggplot(aes(lag, text)) +
  geom_line(aes(color = model)) +
  facet_wrap(~dataset)

hindcast_extent |> 
  copy() |> 
  setnames("aice", "forecast") |> 
  _[, .(forecast = mean(forecast)), by = .(time, forecast_time, lag, model)] |>
  merge(extent_daily) |> 
  _[dataset == which_dataset] |> 
  _[, clim := year(time) %between% c(1981, 2011)] |> 
  _[, let(aice = aice - mean(aice[clim == TRUE]),
          forecast = forecast - mean(forecast[clim == TRUE])),
    by = .(dataset, model, yday(time), forecast_time)] |>
  _[time %between% s1_range] |> 
  _[] |> 
  _[, .(rmse = sqrt(mean((aice - forecast)^2, na.rm = TRUE))), by = .(model, lag, dataset)] |> 
  ggplot(aes(lag, rmse)) +
  geom_line(aes(color = model)) +
  scale_y_continuous(labels = labels_extent)

@@

```{r}
clim_std |> 
  _[obs_dataset == which_dataset] |> 
  _[, .(value = median(climatology, na.rm = TRUE)), by = .(time = update(time, year = 2000))] |> 
  ggplot(aes(time, value)) +
  geom_line()
```

@@

clim_std2 |>
  rbind(errors) |>
  # errors
  _[measure == "rmse"] |> 
  _[obs_dataset == which_dataset] |> 
  _[, .(rmse = median(value, na.rm = TRUE)), 
    by = .(time = update(time, year = 2001), 
           time_forecast = update(time_forecast, year = 2001), 
           lag,
           version)] |> 
  # _[version == "climatology"] |>
  ggplot(aes(time, rmse)) +
  geom_line(data = \(x) x[version == "climatology"],
            aes(group = interaction(time_forecast, month(time_forecast) <= month(time)))) +
  # geom_line(data = \(x) x[version == "S2"],
  #           aes(color = factor(month(time_forecast)),
  #               group = interaction(time_forecast, month(time_forecast) <= month(time)))) +
  # geom_point(data = \(x) x[version == "S2" & lag ==1], aes(color =  factor(month(time_forecast)))) +
  scale_color_manual(values = colorRampPalette(gglgbtq::palette_lgbtq("nonbinary")[c(1, 3, 4, 1)])(12),
                     aesthetics = c("fill", "color"), guide = "none") +
  scale_y_continuous(limits = c(0, NA)) +
  geom_vline(xintercept = as.Date("2001-02-28"))
```

```{r}
clim_std2[version == "climatology"] |> 
  _[obs_dataset == which_dataset] |> 
  _[member == "01"] |>
  _[, .(rmse = median(value, na.rm = TRUE)), 
    by = .(time = update(time, year = 2001), 
           time_forecast = update(time_forecast, year = 2001), 
           lag,
           version)] |>
  ggplot(aes(time, rmse)) +
  geom_line()
